Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-22 paper/paper.tex
Fix issues

Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
that would improve the overall performance of the development team and, inherently, the company. As there are many 
fields in a ticket, there are numerous unanswered questions, such as whether stack traces have an influence on the quality
of a ticket?

In this research paper, we present and discuss our findings after running a quantitative data analysis 
on over 3200,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
from a Jira instance, analyze them, generate plots and run statistical tests.

During the analysis part, we investigate several variables in correlation with \emph{Time-To-Close}, 
which we define as the \emph{metric of quality}. \emph{Time-To-Close} represents the period of time between the creation 
and the closing of a ticket; more specifically, the creation of the ticket is marked when the status of the ticket is set to 
\emph{Open} and the closing of a ticket is considered when the ticket status is set to \emph{Closed} (or some similar status, 
such as \emph{Fixed}, \emph{Resolved}). \emph{Time-To-Close} is our dependent variable, and as independent variables 
(i.e. variables controlled in order to test the effects on the dependent variable) we have set a number of ticket fields.

In order to provide answers to what factors influence quality in a software ticket, we answer the following seven research 
questions in this paper (Section \ref{correlations}):
\begin{itemize}
  \item does the presence of attachments and their type (e.g. code snippet, screenshot) influence the \emph{Time-To-Close} for 
  a ticket?
  \item does the presence of stack traces improve the ticket quality?
  \item does the presence of steps to reproduce reduce the \emph{Time-To-Close}?
  \item is there a relationship between the number of words in comments and \emph{Time-To-Close}?
  \item does the total number of words in summary and description have an impact on \emph{Time-To-Close}?
  \item does the number of grammar errors in summary, description and comments have an effect on the quality of a ticket?
  \item does a positive or negative ticket influence its \emph{Time-To-Close}?
\end{itemize}

@@

In this section we will present what are the state-of-the art studies in the issue/ticket quality 
field. More specifically, we will look at research papers that investigated what makes for a valuable ticket, 
how can one extract structured/unstructured data from tickets (e.g. stack traces), ticket duplication and its 
positive and negative outcomes, quality of modern issue tracking systems as well as automating the process 
of summarizing tickets or the optimal assignee.

@@

Another research paper that strenghtens the argument that readability is a quality 
factor in software tickets is the one presented by Hooimeijer et al. \cite{hooimeijer2007modeling}.
They conducted their analysis on over 25,000 bug reports from the Mozilla project, 
investigating readability, daily load, submitter reputation, the whole changelog histories 
and severity. They conclude that not only readability in the textual fields of a ticket
influence the \emph{Time-To-Close}, but also that the presence of attachments and 
the number of comments have a clear effect on the duration of triaging. On the 
other hand, the patch count and other similar fields did not provide significant 
value to the quality of tickets.

However, there are other types on information typically included in software tickets 
which might prove beneficial for developers and subsequently improve the ticket quality.
One such type is stack traces and Schroter et al. \cite{schroter2010stack} analyse how 
quickly tickets are closed when they either have stack traces included in their fields 
(e.g. description) or not. They collected their data from the Eclipse project using 
the InfoZilla tool proposed by Bettenburg et al. \cite{bettenburg2008extracting}.
Then, they linked the stack traces to changes in source code by mining the Eclipse version 
controlled repository. The results showed that 
around 60\% of the bugs that contained stack traces in their reports were fixed
in one of the methods in the frame. Moreover, more than 40\% of the tickets having stack traces
got fixed in the first stack frame.

Software tickets can have duplicates, usually meaning that the most important fields, such 
as summary or description, describe the same feature request or bug report. Even though 
one might believe that they cannot bring any value to a software project, the work of 
Bettenburg et al. \cite{bettenburg2008duplicate} shows the contrary.
The authors collected large amounts of data from the Eclipse open source project and ran
various kind of textual and statistical analysis on the data to find answers.
After the results were computed, they concluded that usually bug duplicates contain 
information that is not present in the master report (i.e. the original report that was 
filed). Also, developers also specified that they have often found value in these 
duplicate bug reports and that they can even aid automated triaging techniques.

@@

The first information to be filled in by end users or developers on any issue tracking system
is the summary field, which holds a small description, usually between 5 and 30 words, of 
the request or bug being reported. In the study conducted by Rastkar et al. \cite{rastkar2010summarizing}, 
the authors investigated whether tickets could be summarized automatically and efficiently. What 
that implies is that developers would not be required to look at complete tickets comprised 
of a large number of fields, but rather at a simple summary of a couple of lines 
encapsulating the whole information. The authors selected the Mozilla, Eclipse, Gnome and KDE 
open source projects and then they asked volunteering university students to annotate 
the tickets in the issue tracking systems. More specifically, they had to write a summary 
of maximum 250 words using both technical and non-technical terms, depending on their expertise. 
Then, the study presents Machine Learning algorithms employed to parse these summaries and 
learn how to efficiently create automated summaries for new bug reports. Afterwards, they asked 
software developers to rate these auto-generated summaries against the original ones and 
the conclusion was that existing conversation-based extractive summary generators used 
for software tickets produce the best results.

>>>>

Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
that would improve the overall performance of the development team and, inherently, the company. Considering the many fields of 
a ticket, there are numerous elements that could influence its quality, such as the presence of stack traces.

In this research paper, we present and discuss our findings after running a quantitative data analysis 
on over 300,000 tickets taken from more than 38 open source projects. To this aim, we implemented a Go application 
with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
from a Jira instance, analyze them, generate plots and run statistical tests.

For the analysis we investigate several variables in correlation with \emph{Time-To-Close}, 
which we define as the \emph{indicator of quality}. More specifically, an inverse relationship was assigned between the 
two: as \emph{Time-To-Close} increases, the quality decreases. \emph{Time-To-Close} represents the period of time between the creation 
and the closing of a ticket; more specifically, the creation of the ticket is marked when the status of the ticket is set to 
\emph{Open} and the closing of a ticket is considered when the ticket status is set to \emph{Closed} (or some similar status, 
such as \emph{Fixed}, \emph{Resolved}). \emph{Time-To-Close} is our dependent variable, and as independent variables 
(i.e. variables controlled in order to test the effects on the dependent variable) we set a number of ticket fields.

In order to provide answers to what factors influence quality in a software ticket, we investigated the following seven research 
questions in this paper (Section \ref{correlations}):
\begin{itemize}
  \item does the presence of attachments and their type (e.g. code snippet, screenshot) influence the \emph{Time-To-Close} for 
  a ticket?
  \item does the presence of stack traces reduce \emph{Time-To-Close}?
  \item does the presence of steps to reproduce reduce the \emph{Time-To-Close}?
  \item is there a relationship between the number of words in comments and \emph{Time-To-Close}?
  \item does the total number of words in summary and description have an impact on \emph{Time-To-Close}?
  \item does the number of grammar errors in summary, description and comments have an effect on \emph{Time-To-Close}?
  \item does a positive or negative ticket influence its \emph{Time-To-Close}?
\end{itemize}

@@

In this section we will present some of the state-of-the art studies in the issue/ticket quality 
field. More specifically, we will look at research papers that investigated what makes for a high quality ticket, 
how one can extract structured/unstructured data from tickets (e.g. stack traces), ticket duplication and its 
positive and negative outcomes, quality of modern issue tracking systems as well as automating the process 
of summarizing tickets or the optimal assignee.

@@

Another research paper that strenghtens the argument that readability is a quality 
factor in software tickets is the one presented by Hooimeijer et al. \cite{hooimeijer2007modeling}.
They conducted their analysis on over 25,000 bug reports from the Mozilla project, 
investigating readability, daily load, submitter reputation, the whole changelog histories 
and severity. They conclude that not only readability in the textual fields of a ticket
influences the \emph{Time-To-Close}, but also that the presence of attachments and 
the number of comments have a clear lowering effect on the duration of triaging. On the 
other hand, the patch count and other similar fields did not provide significant 
value to the quality of tickets.

However, there are other types of information typically included in software tickets 
which might prove beneficial for developers and subsequently improve the ticket quality.
One such type is stack traces - Schroter et al. \cite{schroter2010stack} analyse how 
quickly tickets are closed depending on whether they have stack traces included in their fields 
(e.g. description) or not. They collected their data from the Eclipse project using 
the InfoZilla tool proposed by Bettenburg et al. \cite{bettenburg2008extracting}.
Then, they linked the stack traces to changes in source code by mining the Eclipse version 
controlled repository. The results showed that 
around 60\% of the bugs that contained stack traces in their reports were fixed
in one of the methods in the frame. Moreover, more than 40\% of the tickets having stack traces
got fixed in the first stack frame.

Software tickets can have duplicates, usually meaning that the most important fields, such 
as summary or description, describe the same feature request or bug report. Even though 
one might believe that they cannot bring any value to a software project, the work of 
Bettenburg et al. \cite{bettenburg2008duplicate} shows the contrary.
The authors collected large amounts of data from the Eclipse open source project and ran
various kinds of textual and statistical analysis on the data to find answers.
After the results were computed, they concluded that usually bug duplicates contain 
information that is not present in the master report (i.e. the original report that was 
filed). The developers also specified that they have often found value in these 
duplicate bug reports and that they can even aid automated triaging techniques.

@@

The first information to be filled in by end users or developers on any issue tracking system
is the summary field, which holds a small description, usually between 5 and 30 words, of 
the request or bug being reported. In the study conducted by Rastkar et al. \cite{rastkar2010summarizing}, 
the authors investigated whether tickets could be summarized automatically and efficiently. What 
that implies is that developers would no longer be required to look at tickets on the whole, comprising of 
a large number of fields, but rather at a simple summary of a couple of lines 
encapsulating the whole information. The authors selected the Mozilla, Eclipse, Gnome and KDE 
open source projects and then they asked volunteering university students to annotate 
the tickets in the issue tracking systems. More specifically, they had to write a summary 
of maximum 250 words using both technical and non-technical terms, depending on their expertise. 
Then, the study presents Machine Learning algorithms employed to parse these summaries and 
learn how to efficiently create automated summaries for new bug reports. Afterwards, they asked 
software developers to rate these auto-generated summaries against the original ones and 
the conclusion was that existing conversation-based extractive summary generators used 
for software tickets produce the best results.
